Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-05-23 paper/synthetic.tex
typo

We evaluate seven metrics:
%
test error in-distribution, test error out-distribution, test error-in distribution after weighting with $\hat{E}$, test error out-distribution after weighting with $\hat{E}$, Sonquist-Morgan false positives on $\hat{E}$, Sonquist-Morgan false negatives on $\hat{E}$, and the area under the ROC curve (AUC) between $\hat{E}$ and $E$.
%
The ``in-distribution'' metrics measure the test error of each predictor before and after weighting their features by the estimated (continous!) mask $\hat{E}$.
%
The ``out-distribution'' metrics are similar, measuring the test error at samples drawn using two different random covariance matrices for both $X$ and $N$.
%
The false positives, false negatives, and AUC statistics measure the quality of identification of causal factors between $\hat{E}$ and the true, binary $E$.

>>>>

We evaluate seven metrics:
%
test error in-distribution, test error out-distribution, test error-in distribution after weighting with $\hat{E}$, test error out-distribution after weighting with $\hat{E}$, Sonquist-Morgan false positives on $\hat{E}$, Sonquist-Morgan false negatives on $\hat{E}$, and the area under the ROC curve (AUC) between $\hat{E}$ and $E$.
%
The ``in-distribution'' metrics measure the test error of each predictor before and after weighting their features by the estimated (continuous!) mask $\hat{E}$.
%
The ``out-distribution'' metrics are similar, measuring the test error at samples drawn using two different random covariance matrices for both $X$ and $N$.
%
The false positives, false negatives, and AUC statistics measure the quality of identification of causal factors between $\hat{E}$ and the true, binary $E$.
